Data for ms. 1

### 2017-03-31 ms1/ms1.Rmd
fixed analysis

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace)
library(assertive)
```

```{r setup}
# Group values in x into ranges determined by upper_limits.
# Values below the lowest limit are named as the lowest limit, and so forth.
# You should probably put Inf as the last limit.
bounds_group = function(x, upper_limits) {
  levels = lapply(seq(from=1, to=length(upper_limits)), function(i) {
    if (i == 1) {
      sprintf('< %.1f', upper_limits[i])
    } else {
      sprintf('>= %.1f and < %.1f', upper_limits[i - 1], upper_limits[i])
    }
  })
  formula_list = mapply(function(str, lim) as.formula(sprintf('x < %.1f ~ "%s"', lim, str)),
                        levels, upper_limits)
  do.call(case_when, formula_list) %>%
    factor(levels=levels, ordered=TRUE)
}

@@

  # characteristics by consumption
  cc = read_tsv(sprintf('../../data/cc_%i.tsv', this_year))

@@

  claims_group_f = function(x) bounds_group(x, c(0, 1, 5, 10, 20, Inf))
  chars_by_consumption = usage %>%
    mutate(claims_group=claims_group_f(n_claims)) %>%
    group_by(claims_group) %>%
    summarize(`no. beneficiaries`=n(),
              `mean age`=mean(age),
              `% female`=mean(is_female),
              `mean no. chronic conditions`=mean(n_cc)) %>%
    mutate(year=this_year)

@@

chars_by_consumption = data_by_field('chars_by_consumption') %>%
  arrange(desc(y), desc(claims_group)) %>%
  kable

>>>>

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace)
library(assertive)
```

```{r setup, cache=FALSE}
# Group values in x into ranges determined by upper_limits.
# Values below the lowest limit are named as the lowest limit, and so forth.
# You should probably put Inf as the last limit.
bounds_group = function(x, upper_limits) {
  levels = lapply(seq(from=1, to=length(upper_limits)), function(i) {
    if (i == 1) {
      sprintf('< %.1f', upper_limits[i])
    } else {
      sprintf('>= %.1f and < %.1f', upper_limits[i - 1], upper_limits[i])
    }
  })
  formula_list = mapply(function(str, lim) as.formula(sprintf('x < %.1f ~ "%s"', lim, str)),
                        levels, upper_limits)
  do.call(case_when, formula_list) %>%
    factor(levels=levels, ordered=TRUE)
}

@@

  # characteristics by consumption
  cc = read_tsv(sprintf('../cc_%i.tsv', this_year))

@@

  claims_group_f = function(x) bounds_group(x, c(1, 2, 5, 10, 20, Inf))
  chars_by_consumption = usage %>%
    mutate(claims_group=claims_group_f(n_claims)) %>%
    group_by(claims_group) %>%
    summarize(`no. beneficiaries`=n(),
              `mean age`=mean(age),
              `% female`=mean(is_female) * 100,
              `mean no. chronic conditions`=mean(n_cc)) %>%
    mutate(year=this_year)

@@

chars_by_consumption = data_by_field('chars_by_consumption') %>%
  arrange(desc(year), desc(claims_group)) %>%
  kable
